\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-02 metatheory-condensed.tex
Inser CC-condensed inplace.
Venn diagram

When a family is completed (e.g., \lsti!End!~\lsti!STLC!),
a linkage~$\lkg$ containing all the fields is available
(e.g., $\lkg_{20}$ in \cref{fig:stlc-linkage-typing}).
Fields of the family can then be accessed by projecting them out of the tuple
$\Tkg{\lkg}$.

@@

>>>>

When a family is completed (e.g., \lsti!End!~\lsti!STLC!),
a linkage~$\lkg$ containing all the fields is available
(e.g., $\lkg_{53}$ in \cref{fig:stlc-linkage-typing}).
Fields of the family can then be accessed by projecting them out of the tuple
$\Tkg{\lkg}$.

@@

\input{cc-condensed.tex}
